Toronto Paramedic Services

### 2024-09-25 paper/paper.qmd
the shape file wouldn't open so tried deleting the folder and replacing it with just the shape file.
tried reading in the shapefile again - did not work
successfully loaded shapefile!
working on the code to map

>>>>

## Mapping EMS Demand

```{r}
#| echo: false 
#| message: false
#| label: fig-map
#| fig-cap: EMS Demand Across Toronto Forward Sortation Areas (Based on data from 2022)

library(maps)
library(sf)

# Reading in the shapefile
toronto_forward_sortation_areas <- st_read("~/Toronto_Paramedic_Services/data/TorontoForwardSortationAreas")

# Reading in the data to show in map
data <- read_csv("data/analysis_data/analysis_data_FOR_MAP.csv")
